---
title: "Get started with psychdsish"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with psychdsish}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(psychdsish)
```

`psychdsish` helps you set up and check research projects that follow a
standardised, reproducibility-friendly layout. The layout is loosely inspired
by the [psych-DS](https://psych-ds.github.io/) data standard, but is
deliberately *not* fully psych-DS compliant -- most notably it drops the JSON
metadata requirement. Hence *psych-DS-ish*.

There are three things you will usually do:

1. **Create** a project skeleton with `create_project_skeleton()`.
2. **Validate** an existing project against the conventions with `validator()`.
3. (rarely, and mainly for testing) **Delete** a skeleton with
   `delete_project_skeleton()`.

## Creating a project skeleton

`create_project_skeleton()` writes an opinionated directory tree together with a
`README`, a licence, a `.gitignore` with sensible defaults, and Quarto
templates for processing and analysis code.

If you know the path to your project you can call it directly from the console:

```{r, eval = FALSE}
create_project_skeleton(project_root = "~/git/my_project")
```

The default `project_root = "../"` assumes you are running it from a
`project_name/tools/project_creator.qmd` file, so that the skeleton is written
to the project root one level up.

Here is a complete, self-contained round-trip inside a temporary directory:

```{r}
project <- file.path(tempdir(), "demo_project")

create_project_skeleton(project_root = project, overwrite = TRUE)

# the top-level layout that was created
list.dirs(project, recursive = FALSE, full.names = FALSE)
```

The skeleton separates raw data, processed data, analysis code, outputs, and
documentation:

```text
my_project/
├── .gitattributes
├── .gitignore
├── LICENSE
├── README.md
├── code/
│   ├── analysis.qmd
│   └── processing.qmd
├── data/
│   ├── outputs/
│   │   ├── fitted_models/
│   │   ├── plots/
│   │   └── results/
│   ├── processed/
│   └── raw/
├── methods/
├── preregistration/
└── reports/
```

## Validating a project

`validator()` checks a project against the psych-DS-ish conventions and returns
a table of tests, each marked `PASS` or `FAIL`, with guidance on how to fix any
failures. A freshly created skeleton passes every test:

```{r}
res <- validator(project_root = project)
res
```

The rules cover, among other things, which directories must exist, where each
file type is allowed to live (for example, data files under `data/`, scripts
under `code/` or `tools/`), and that filenames contain no spaces. See
`?validator` for the full set of rules.

## Deleting a skeleton

`delete_project_skeleton()` exists mainly for testing. It is deliberately
cautious: by default it requires interactive confirmation and the presence of a
"sentinel" file (such as `.gitignore`) so that you cannot point it at an
arbitrary directory by accident. Always preview with `dry_run = TRUE` first.

```{r}
# preview only -- nothing is removed
invisible(delete_project_skeleton(project_root = project, confirm = FALSE, dry_run = TRUE))

# actually remove the demo project (non-interactive)
delete_project_skeleton(project_root = project, confirm = FALSE)

dir.exists(project)
```

## Where to go next

- `?create_project_skeleton` for every directory and template that is created.
- `?validator` for the complete list of validation rules.
- The package also ships small helpers for tidying code style
  (`style_all_files()`, `print_poorly_styled_code()`) and for spotting unused
  dependencies and objects (`check_unused_dependencies()`,
  `check_unused_objects()`).
